\documentclass[english]{article}

\usepackage{graphicx}
\usepackage{grffile}
\usepackage{babel}

\author{
	Abhinav Thakur\\
	\texttt{13286383}
	\and
	Akua Afrane-Okese\\
	\texttt{15019773}
	\and
	Brian Kamau Ndung’u\\
	\texttt{15322913}
	\and
	Linda Zwane\\
	\texttt{14199468}
	\and
	Ntiko Mathaba\\
	\texttt{14012503}
	\and
	Tyler Matthews\\
	\texttt{15302424}
}	

\title{Arivl App User Manual\\}

\graphicspath{{Pictures/}}

\begin{document}
	\maketitle
	
	\pagenumbering{gobble}
	\newpage

	\tableofcontents
	\newpage

	\pagenumbering{arabic}
	

	\section{Arivl}
		\paragraph\indent
			

		\subsection{System Overview}
			\paragraph\indent
What Arivl entails is the ability to open boom gates of places, namely homes, malls, and work with the swipe on a phone- which is on Bluetooth (specifically Bluetooth Low Energy). 

		\subsection{System Configuration}
			\paragraph\indent
				Bluetooth needs to be set to “on” on the smartphone of the user. Once a BLE connection is established, your Arivl device will search for the closest boom to the location of the user. On the boom is an ArivlBox and when the phone connects to the box, then the user has to swipe the phone.  

		\subsection{Installation}
			\paragraph\indent
The person who wants access a particular place must install the Arivl Application onto their smartphone. 

		\subsection{Getting Started}
			\paragraph\indent
The user needs to enter their details onto the Arivl application.

		\subsection{Using the System}
			\paragraph\indent
The user will be faced with a login button, which asks the users to enter in their phone number. After the phone is verified, the user is taken to the home page.				
		\subsection{Troubleshooting}
		\paragraph\indent
The application uses Bluetooth thus will not work if Bluetooth is not connected.
				

	

	

		
\end{document}
